Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-11 ms.tex
Update Section 5 and MWACS paper reference
From 1d3cd47:
============

In ms.tex,

(*) Update Section 5

In eor.bib,

(*) Update reference to MWACS paper

Using deeper MWA data, we have confirmed with high significance the earlier prediction that wide-field EoR measurements suffer significant foreground contamination from near the horizon. This has important implications for instrument design and data analysis of future instruments such as HERA and SKA.

Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds. All-sky surveys matching the frequency and angular resolution of observation, and a detailed model of the instrument will further improve the accuracy of our models. In our earlier study, we proposed a selective flagging of data on different antenna spacings that can potentially mitigate foreground contamination by two orders of magnitude. Efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis algorithms.

For future work, we plan to extend our analysis to the upcoming instrument, HERA, which is currently under construction. It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings. Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint. One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.

>>>>

Using deeper MWA data, we have confirmed with high significance the earlier prediction that wide-field EoR measurements suffer significant foreground contamination from near the horizon. This has important implications for instrument design and data analysis of future instruments such as HERA and SKA. For instance, SKA plans to use vertical log-periodic dipole arrays while HERA will use dishes that limit response near the horizon. Details of both telescopes are being finalized.

Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds. Extending the footprint of surveys matching the frequency and angular resolution of observation such as the MWA Commissioning Survey \citep[MWACS;][]{hur14} and the Galactic and Extragalactic MWA Survey (GLEAM; Hurley-Walker et al. in prep.) to cover the entire hemisphere, and a detailed model of the instrument will further improve the accuracy of our models. In our earlier study, we proposed a selective flagging of data on different antenna spacings that can potentially mitigate foreground contamination by two orders of magnitude. Following the confirmation presented here, efforts are underway to incorporate this proposed foreground mitigation technique into the MWA data analysis algorithms.

For future work, we plan to extend our analysis to HERA. It is a closely packed hexagonal array of fixed 14~m dishes which will observe the sky drifting overhead with redundant antenna spacings. Based on our earlier study, such a dish will have a much desirable Fourier response from a foreground contamination viewpoint. One of our objectives is to forecast the per-baseline foreground contamination as a function of local sidereal time in order to tune the HERA observing strategy and data analysis to maximize sensitivity to the EoR signal.
